A prototype software framework for transparent, reusable and updatable computational health economic models

### 2023-10-22 Reports/Manuscript/Tex_Export/Manuscript.tex
problems with table and figure placement

\caption{\label{tab:cpkgs}Software framework R libraries}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
\toprule
Package & Purpose & R library dependencies\\
\midrule
ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs. & assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms. & desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules. & devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured. & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories. & data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
\addlinespace
ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines. & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=400px]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
\end{figure}

>>>>

\caption{\label{tab:cpkgs}Software framework R libraries}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
\toprule
Package & Purpose & R library dependencies\\
\midrule
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4_logo.png} & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs. & assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4fun_logo.png} & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms. & desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4class_logo.png} & Streamline and standardise the authoring and documenting of new interoperable CHEM modules. & devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4pack_logo.png} & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured. & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4use_logo.png} & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories. & data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
\addlinespace
\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4show_logo.png} & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines. & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=400px]{Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
\end{figure}
